## Weekly Transformative Agreement Data dumps

This repo contains weekly dumps of [public transformative agreement data](https://journalcheckertool.org/transformative-agreements/) as provided by the [Journal Checker Tool](https://journalcheckertool.org/) from the [cOAlition S](https://www.coalition-s.org/). 


## Data

Data are stored in the `data/` folder, comprising two files

- `data/jct_journals.csv`: complete dump of journals metadata associated with transformative agreements
- `data/jct_institutions.csv`: complete dump of institutions metadata associated with transformative agreements

## Snapshots

```{r, results='asis', message=FALSE, echo=FALSE}
library(gert)
library(dplyr)
library(knitr)


gert::git_log() |>
  dplyr::filter(time > as.POSIXct("2022-12-22")) |>
  dplyr::filter(grepl("Update data", message)) |>
  dplyr::mutate(link = paste0("<a href='https://github.com/njahn82/jct_data/tree/", commit, "/data'>",commit, "</a>")) |>
  dplyr::select(`Time updated` = time, `Snapshot` = link) |>
  knitr::kable()
```

## Latest stats as on `r Sys.Date()`

```{r echo =FALSE, message=FALSE, warning=FALSE}
jct_journals <- readr::read_csv("data/jct_journals.csv")
jct_institutions <- readr::read_csv("data/jct_institutions.csv")
```

- `r length(unique(jct_journals$esac_id))` transformative agreements with ESAC ID
- `r format(length(unique(jct_journals$journal_name)), big.mark=",")` journal titles covered
- `r format(length(unique(jct_institutions$inst_name)), big.mark=",")` institutions participating
- `r format(length(unique(jct_institutions$ror_id)), big.mark=",")` institutions covered have a ROR-ID

## License

CCO