## Weekly Transformative Aggreement Data dumps

This repo contains weekly dumps of [public transformative agreement data](https://journalcheckertool.org/transformative-agreements/) as provided by the [Journal Checker Tool](https://journalcheckertool.org/) from the [cOAlition S](https://www.coalition-s.org/). 

## Data

Data are stored in the `data/` folder, comprising two files

- `data/jct_journals.csv`: journals and their properties
- `data/jct_institutions.csv`: institutions and their properties

## Snapshots

```{r, results='asis', message=FALSE, echo=FALSE}
library(gert)
library(dplyr)
library(knitr)

gert::git_log() |>
  dplyr::filter(time > as.POSIXct("2022-12-22")) |>
  dplyr::filter(grepl("Update data", message)) |>
  dplyr::select(`Time updated` = time, `Snapshot` = commit) |>
  knitr::kable()
```

## Latest Stats as on `r Sys.Date()`

```{r echo =FALSE, message=FALSE}
jct_journals <- readr::read_csv("data/jct_journals.csv")
jct_institutions <- readr::read_csv("data/jct_institutions.csv")
```

- `r length(unique(jct_journals$esac_id))` transformative agreements with ESAC ID
- `r length(unique(jct_journals$journal_name))` journal titles covered
- `r length(unique(jct_institutions$inst_name))` institutions participating 
- `r length(unique(jct_institutions$ror_id))` institutions covered have a ROR-ID

## License

CCO