
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark=",")
})

library(dplyr)
library(readr)

jct_journals <- readr::read_csv("data/jct_journals.csv")
jct_institutions <- readr::read_csv("data/jct_institutions.csv") |>
  mutate(inst_first_seen = as.Date(inst_first_seen))
```

## Data Snapshot `r as.character(Sys.Date())`

This release provides a snapshot of publicly available transformative agreement data as provided by the cOAlition S Journal Checker Tool on **`r as.character(Sys.Date())`**.

This release contains two files

### `jct_journals.csv`

```{r, results='asis'}
jct_journals |>
  head() |>
  knitr::kable()
```

- `jct_institutions.csv`: institutions and their properties

```{r, results='asis'}
jct_institutions |>
  head() |>
  knitr::kable()
```

The files are stored in the `data` folder and attached to this GitHub release.

## Stats

- `r length(unique(jct_journals$esac_id))` transformative agreements with ESAC ID
- `r length(unique(jct_journals$journal_name))` journal titles covered
- `r length(unique(jct_institutions$inst_name))` institutions participating 
- `r length(unique(jct_institutions$ror_id))` institutions covered have a ROR-ID


## LICENSE

CC-O




